---
title: "DS105M: Women In Parliament - Data"
author: AS, NC, LM
date: November 26, 2021
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{css echo=FALSE}
h1 {
text-align: center;
color:tomato;
font-size: 29px;
font-weight:bold;
align-self: center;
text-align: center;
}
div {font-size: 24px;
letter-spacing: 2px;
word-spacing: 2.5px;
text-decoration: none;
font-style: normal;
font-variant: normal;
text-transform: none;
padding-top: 20px;
}
ul, p {
padding: 1px 2% 1px;
max-height:90%
text-align: ltr;
font-weight: normal;
color: #1E1E1E;
}
* {background-color: #EDEDED;
background-size: 100%;
font-family: "Lucida Console", Monaco, monospace;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=FALSE}
if(!require("pacman"))install.packages("pacman")

pacman::p_load("tidyverse", "reticulate", "here")
```


```{r data, include=FALSE}
#source(here("scripts", "download-csv-html.R")) # once you have run the script once, you can comment out this line by typing "#" in front of it. Doing this will mean the data loads directly from your local data_raw folder rather than downloading every time.

harvard <- read.csv(here("data_raw", "rawdata.csv"))

#source_python(here("scripts", "test.py"))
```

## Brief summary

* Our project looks at the relative proportions that MPs speak in the Scottish Parliament.

## Organisation of the project

* Guiding principle: reproducibility

* Source code of everything we produce avaliable on GitHub
  * The user only has to have RStudio and Python installed on their machine to run it all

* Any user able to download the repo and run
  * Programmatic data download and cleaning



## Workflow

* Division of labour
  * Alanah was working mainly on the HTML / CSS code chunk of the presentation
  * Noemie was working on wragling data
  * Len was working on the Rmarkdown

* GitHub was the solution
  * Everyone using different text editors
    * Noemie: Spyder
    * Alanah: GitHub, RStudio
    * Len: Atom, RStudio
  * Each have a branch
  * No matter what we were using we can all commit changes from terminal (or via the application we are using)
  * Also allowed us to see entire version control





## Main data collection and cleaning

## Expansion

We wanted to compare speech time in Parliament with tweet frequency for each MP.

Our process would have been:

* Scrape MP tweet_ids from Wiki-data. Wiki-IDs are included as document metadata so we could have written a program that finds the relevant tweet ID from each politician.

* Pull timelines for each politician

However, API licence doesn't allow this - is that true?


```{r}
speeches <- subset(harvard, harvard$is_speech == 1)
```

## Summary statistics on speeches

Some key facts about the speeches:

* There were `r nrow(speeches)` speeches.
* `r nrow(subset(speeches, speeches$gender == "F"))` of the speeches were by women.
* `r (nrow(subset(speeches, speeches$gender == "F"))/ nrow(speeches))*100`% of the speeches in our sample were by women.

## Summary statistics on MSPs

```{r}
msps <- speeches %>% select(name, gender)

msps <- unique(msps)

msps <- drop_na(msps)
```


Some facts about the MSPs in our sample

* There were a total of `r nrow(msps)` in our sample

* `r nrow(subset(msps, msps$gender == "F"))` were women

* Therefore, `r (nrow(subset(msps, msps$gender == "F"))/ nrow(msps))*100`% of the MSPs in out sample are women.


## Data Analysis

### Tools
* R
  * Downloading the raw data progromatically
  * Summary statistics for presentations

* Python
  * Formatting the dataset
  * * NLP of sylablles

## What we want to visualise

## Change in gender differences of speech time over the years

* Stacked column graph

* Variables: gender (m/f, columns), speech time (%, y axis), years (x axis)

* Interactive element: cursor moves across graph to show exact % each year, and any outstanding events

## Power in parliament represented by amount of seats taken up once gender differences in speech time is considered

* Scottish parliamentary seat map
  * GIS data matched to constituency name (relational data)

* Variables: gender (m/f), speech time (%)

* Interactive element: can click between actual number of seats and the speech-time-factored-in number of seats

## Absolute gender difference in amount of speech

* 'Men'/'women' speech bubbles

* Variables: gender (m/f), speech time (%)

## Proportions of time men and women speak

* Circle chart

* Variables: gender (m/f), speech time (%)

## What tools we're using

* Tableau Public
