---
title: 'DS105M: Women In Parliament - Data'
author: AS, NC, LM
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=FALSE}
if(!require("pacman"))install.packages("pacman")

pacman::p_load("reticulate", "here")
```


```{r data, include=FALSE}
#source(here("scripts", "download-csv-html.R")) # once you have run the script once, you can comment out this line by typing "#" in front of it. Doing this will mean the data loads directly from your local data_raw folder rather than downloading every time. 

harvard <- read.csv(here("data_raw", "rawdata.csv"))

source_python()
```


## Brief summary 

Our project looks at the relative proportions that MPs speak in the Scottish Parliament. 

## Organisation of the project

* Guiding principle: reproducibility 

* Source code of everything we produce avaliable on GitHub 
  * Is why we coded slides 
  
* Any user able to download the repo and run
  * Programmatic data download and cleaning 


## Main data collection and cleaning 

## Expansion 

We wanted to compare speech time in Parliament with tweet frequency for each MP. 

Our process would have been: 

* Scrape MP tweet_ids from Wiki-data. Wiki-IDs are included as document metadata so we could have written a program that finds the relevant tweet ID from each politician. 

* Pull timelines for each politician 

However, API licence doesn't allow this - is that true?







