---
title: 'DS105M: Women In Parliament - Data'
author: AS, NC, LM
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=FALSE}
if(!require("pacman"))install.packages("pacman")

pacman::p_load("reticulate", "here")
```

```{r set project root}
# The project root is the local folder which you have cloned the speech-time repo to. Set whatever that folder is on your machine here: 

knitr::opts_knit$set(root.dir = '"C:/Users/lenna/OneDrive - London School of Economics/year_3/Courses/MT_DS105M_Data-for-Data-Science/project/speech-time')

```


```{r data, include=FALSE}
source(here("scripts", "download-csv-html.R"))

source_python()
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with Py Output


## Slide with Plot

```{r pressure}
plot(pressure)
```

