---
title: "DS105M: Women In Parliament - Data"
author: AS, NC, LM
date: November 26, 2021
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{css echo=FALSE}
h1 {
text-align: center;
color:tomato;
font-size: 29px;
font-weight:bold;
align-self: center;
text-align: center;
}
div {font-size: 24px;
letter-spacing: 2px;
word-spacing: 2.5px;
text-decoration: none;
font-style: normal;
font-variant: normal;
text-transform: none;
padding-top: 20px;
}
ul, p {
padding: 1px 2% 1px;
max-height:90%
text-align: ltr;
font-weight: normal;
color: #1E1E1E;
}
* {background-color: #EDEDED;
background-size: 100%;
font-family: "Lucida Console", Monaco, monospace;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r packages, include=FALSE}
if(!require("pacman"))install.packages("pacman")

pacman::p_load("tidyverse", "reticulate", "here")
```


```{r data, include=FALSE}
#source(here("scripts", "download-csv-html.R")) # once you have run the script once, you can comment out this line by typing "#" in front of it. Doing this will mean the data loads directly from your local data_raw folder rather than downloading every time.

harvard <- read.csv(here("data_raw", "rawdata.csv"))
```
# Slide 1.1: Brief summary

# Slide 1.2: Organisation

# Slide 1.3: Workflow

# Slide 2.1: Obtaining the data

# Slide 2.2: Summary statistics

# Slide 2.3: Summary statistics on speeches

# Slide 2.4: Summary statistics on msps

# Slide 3.1: Data wrangling
1. **Data cleaning**
  + Subset the semi-structured dataset to keep only the relevant information
  + Discard information irrelevant to our analysis
2. **Improving data accuracy**
  + Strip the data of missing values
  + Cross-check summary statistics results across R and python
  + Ensure consistency in results across languages
3. **Partition and export the dataframe to the repository**
  + Result: structured, relational data ready to be used for analysis
  + Partitions of dataframe can be used to count the number of syllables spoken by MSPs and compare the obtained values between men and women

# Slide 3.2: Analysis
Some insights we'd like to draw from the data:
* Average and median number of syllables by gender
* Whether this discrepency also exists on Twitter
* See if gender-related lexic is found at a higher rate in women's speeches than in men's speeches (using sentiment analysis)

# Slide 3.3: Visualisations planned
| What we're planning to visualise                                                                                   | Graph                           | Variables                                                      |
|-------------------------------------------------------------------------------------------------------------------|---------------------------------|----------------------------------------------------------------|
| Change in gender differences of speech time over the years                                                        | Stacked column graph            | gender (m/f, columns), speech time (%, y axis), years (x axis) |
| Power in parliament represented by amount of seats taken up once gender differences in speech time are considered | Scottish parliamentary seat map | gender (m/f), speech time (%)                                  |
| Relationship between speech time and age                                                                          | Scatter graph                   | gender (m/f), speech time (n)                                  |
| Absolute gender differences in amount of speech                                                                   | Speech bubbles                  | gender (m/f), speech time (%)                                  |
| Proportions of time men and women speak                                                                           | Circle chart                    | gender (m/f), speech time (%)                                  |
| Party comparison of women speech time                                                                             | Stacked bar chart               | gender (m/f, bars), MP political party (y axis),               |
| Comparison of Twitter activity and speech time                                                                    | Line graph                      | speech time (n, y axis), Twitter followers (n, x axis)         |
| Regional differences in gender speech times                                                                    | Heat map                      | speech time (%), gender (m/f)         |

**Tools we're planning on using:**
* Tableau Public
* SQL
